Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-03 paper.tex
Add empty figure for CAD drawing

In this study we seek to predict the near-wake of the UNH-RVAT turbine,
experimental performance curves for which are shown in
Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient, and a turbine
diameter Reynolds number $Re_D \approx 10^6$, which corresponds to a
$Re$-independent state for both performance and near-wake characteristics, as
determined from experimental measurements \cite{Bachant2014,
    Bachant2015-RVAT-Re-dep}.

>>>>

In this study we seek to predict the near-wake of the UNH-RVAT turbine, shown in
Figure~\ref{fig:RVAT-CAD}. Experimental performance curves for the UNH-RVAT are
shown in Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient, and a turbine
diameter Reynolds number $Re_D \approx 10^6$, which corresponds to a
$Re$-independent state for both performance and near-wake characteristics, as
determined from experimental measurements \cite{Bachant2014,
    Bachant2015-RVAT-Re-dep}.

    \caption{CAD model of the UNH-RVAT cross-flow turbine}

    \label{fig:RVAT-CAD}
\end{figure}
